---
title: "campaign finance"
author: "remy sorensen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r }
library(tidyverse)
library(ggplot2)
library(DataExplorer)
library(tidyverse)
library(lubridate)
library(colorspace)
```



```{r}
#2020 donors by state

CA_data <- data.frame(California = c(State_Donor_Total=1184582383, House_Total=177064633, Senate_Total=198947319, Pres_Total=191438455,	PAC_Total=473013762, Party_Total=77040874, Total_527=67077340))

NY_data <- data.frame(NewYork = c(State_Donor_Total=654505644, House_Total=106283545, Senate_Total=96729357, Pres_Total=92257835,	PAC_Total=288022300, Party_Total=43426149, Total_527=27786458))

TX_data <- data.frame(Texas	= c(State_Donor_Total=505431584, 	House_Total=98553277, Senate_Total=93450362, Pres_Total=58273294, 	PAC_Total=193475434, Party_Total=38695665, Total_527=22983552)) 

FL_data <- data.frame(Florida = c(State_Donor_Total=399825186, House_Total=72198411, Senate_Total=72076565, Pres_Total=50748059, PAC_Total=151778296, Party_Total=335549583, Total_527=17474272)) 

VA_data <- data.frame(Virginia = c(State_Donor_Total=346444371, House_Total=37228571, Senate_Total=56894484, Pres_Total=66332812, 	PAC_Total=155870792, Party_Total=14621957, Total_527=15495755)) 
```


```{r}
MA_data <- data.frame(Massachusetts = c(State_Donor_Total=287103211, House_Total=336493783, Senate_Total=53618079, Pres_Total=43928513, PAC_Total=76402559, Party_Total=15289535, Total_527=61370742))

IL_data <- data.frame(Illinois = c(State_Donor_Total=245890949, House_Total=41154462, Senate_Total=36905984, Pres_Total=33496079, PAC_Total=101624791, Party_Total=15418509, Total_527=17291124)) 
```

```{r}
WA_data <- data.frame(Washington = c(State_Donor_Total=182235165, House_Total=27038289, Senate_Total=36095051, Pres_Total=42150043, PAC_Total=51603520, Party_Total=16713922, Total_527=8634340))

PA_data <- data.frame(Pennsylvania = c(State_Donor_Total=179872874, House_Total=28249423, Senate_Total=326350387, Pres_Total=31076181, PAC_Total=71587849, Party_Total=13362129, Total_527=9246905))

GA_data <- data.frame(Georgia	= c(State_Donor_Total=171989122, House_Total=23257467, Senate_Total=52686149, Pres_Total=317804539, PAC_Total=56877581, Party_Total=11581532, Total_527=9781854)) 

MD_data <- data.frame(Maryland = c(State_Donor_Total=138320653, House_Total=21075240, Senate_Total=27640352, Pres_Total=26818450, PAC_Total=45112869, Party_Total=11145649, Total_527=6528093)) 
```

_data <- data.frame( = c(State_Donor_Total=, House_Total=, Senate_Total=, Pres_Total=,	PAC_Total=, Party_Total=, Total_527=))

```{r}
MI_data <- data.frame(Michigan = c(State_Donor_Total=134933612, House_Total=23148344, Senate_Total=33626118, Pres_Total=17505203, PAC_Total=39816994, Party_Total=15106017, Total_527=5730936)) 
```

```{r}
NJ_data <- data.frame(NewJersey = c(State_Donor_Total=34176446, 
                           House_Total=29032234, 
                           Senate_Total=21514450, 
                           Pres_Total=26433905,	
                           PAC_Total=42148291, 
                           Party_Total=8728694, 
                           Total_527=6318872))

CO_data <- data.frame(Colorado = c(State_Donor_Total=126278129, 
                           House_Total=17613214, 
                           Senate_Total=37092516, 
                           Pres_Total=24012848,	
                           PAC_Total=35089016, 
                           Party_Total=8230309, 
                           Total_527=4240226))

```




```{r}
OH_data <- data.frame(Ohio = c(State_Donor_Total=124466184, 
                           House_Total=18681390, 
                           Senate_Total=19054436, 
                           Pres_Total=17111332,	
                           PAC_Total=45317804, 
                           Party_Total=13329981, 
                           Total_527=10971241))

NC_data <- data.frame(NorthCarolina = c(State_Donor_Total=116413361, 
                           House_Total=19631749, 
                           Senate_Total=25227845, 
                           Pres_Total=18982327,
                           PAC_Total=30716530, 
                           Party_Total=10559864, 
                           Total_527=11295046))

AZ_data <- data.frame(Arizona = c(State_Donor_Total=99393014, 
                           House_Total=15600074, 
                           Senate_Total=35566685, 
                           Pres_Total=14977528,	
                           PAC_Total=21509679, 
                           Party_Total=8249942, 
                           Total_527=3489106))


CT_data<- data.frame(Connecticut = c(State_Donor_Total=96989613, 
                           House_Total=11125971, 
                           Senate_Total=17380720, 
                           Pres_Total=14204573,	
                           PAC_Total=38879760, 
                           Party_Total=7699484, 
                           Total_527=7699105))

MN_data <- data.frame(Minnesota = c(State_Donor_Total=93176647, 
                           House_Total=17185592, 
                           Senate_Total=16082607, 
                           Pres_Total=16350466,	
                           PAC_Total=28899908, 
                           Party_Total=7981349, 
                           Total_527=6676725))

TN_data <- data.frame(Tennessee = c(State_Donor_Total=92201769, 
                           House_Total=12580044, 
                           Senate_Total=22909167, 
                           Pres_Total=1114834,	
                           PAC_Total=27938244, 
                           Party_Total=9710873, 
                           Total_527=7915100))

NV_data <- data.frame(Nevada = c(State_Donor_Total=89747751, 
                           House_Total=9583638, 
                           Senate_Total=9936602, 
                           Pres_Total=7714253,	
                           PAC_Total=45768222, 
                           Party_Total=5335294, 
                           Total_527=11409742))

MO_data<- data.frame(Missouri = c(State_Donor_Total=78454209, 
                           House_Total=12807144, 
                           Senate_Total=12933900, 
                           Pres_Total=9185795,	
                           PAC_Total=23419869, 
                           Party_Total=7251341, 
                           Total_527=12856160))

IN_data<- data.frame(Indiana = c(State_Donor_Total=68829914, 
                           House_Total=10425093, 
                           Senate_Total=10294201, 
                           Pres_Total=9382112,	
                           PAC_Total=28191129, 
                           Party_Total=5178046, 
                           Total_527=5359333))

WI_data<- data.frame(Wisconsin = c(State_Donor_Total=64077237, 
                           House_Total=12434894, 
                           Senate_Total=9354142, 
                           Pres_Total=9462439,	
                           PAC_Total=19143554, 
                           Party_Total=7394209, 
                           Total_527=6287999))


```



```{r}

OR_data <- data.frame(Oregon = c(State_Donor_Total=60988553, 
                           House_Total=9359526, 
                           Senate_Total=15745802, 
                           Pres_Total=17173061,	
                           PAC_Total=11538387, 
                           Party_Total=6239658, 
                           Total_527=932119))


LA_data<- data.frame(Louisiana = c(State_Donor_Total=57297331, 
                           House_Total=12254437, 
                           Senate_Total=11065298, 
                           Pres_Total=5397856,	
                           PAC_Total=21505851, 
                           Party_Total=3695258, 
                           Total_527=3378631))

AL_data<- data.frame(Alabama = c(State_Donor_Total=54073317, 
                           House_Total=10497848, 
                           Senate_Total=16495444, 
                           Pres_Total=5089898,	
                           PAC_Total=15943662, 
                           Party_Total=5238865, 
                           Total_527=807600))


```

```{r}

SC_data<- data.frame(SouthCarolina = c(State_Donor_Total=50894265, 
                           House_Total=11735187, 
                           Senate_Total=15927595, 
                           Pres_Total=7612454,	
                           PAC_Total=10599809, 
                           Party_Total=4248484, 
                           Total_527=770736))


OK_data<- data.frame(Oklahoma = c(State_Donor_Total=45900741, 
                           House_Total=10127429, 
                           Senate_Total=8993648, 
                           Pres_Total=4996197,	
                           PAC_Total=13799497, 
                           Party_Total=4796090, 
                           Total_527=3187880))


```



```{r}

KY_data<- data.frame(Kentucky = c(State_Donor_Total=40895555, 
                           House_Total=5192308, 
                           Senate_Total=8823752, 
                           Pres_Total=4631498,	
                           PAC_Total=10891856, 
                           Party_Total=8017582, 
                           Total_527=3338559))


IA_data<- data.frame(Iowa = c(State_Donor_Total=39668386, 
                           House_Total=9469899, 
                           Senate_Total=9061897, 
                           Pres_Total=4912752,	
                           PAC_Total=9319348, 
                           Party_Total=4681317, 
                           Total_527=2223173))

KS_data<- data.frame(Kansas = c(State_Donor_Total=39582393, 
                           House_Total=8324906, 
                           Senate_Total=11579586, 
                           Pres_Total=4070707,	
                           PAC_Total=10345901, 
                           Party_Total=3154749, 
                           Total_527=2106544))

NM_data <- data.frame(NewMexico = c(State_Donor_Total=35113356, 
                           House_Total=9261391, 
                           Senate_Total=9605079, 
                           Pres_Total=6386308,	
                           PAC_Total=5911455, 
                           Party_Total=2938670, 
                           Total_527=1010453))

```
<- data.frame( = c(State_Donor_Total=, 
                           House_Total=, 
                           Senate_Total=, 
                           Pres_Total=,	
                           PAC_Total=, 
                           Party_Total=, 
                           Total_527=))

```{r}

NM_data <- data.frame(NewMexico = c(State_Donor_Total=35113356, 
                           House_Total=9261391, 
                           Senate_Total=9605079, 
                           Pres_Total=6386308,	
                           PAC_Total=5911455, 
                           Party_Total=2938670, 
                           Total_527=1010453))


AR_data <- data.frame(Arkansas = c(State_Donor_Total=31287895, 
                           House_Total=5820860, 
                           Senate_Total=5173979, 
                           Pres_Total=3041153,	
                           PAC_Total=10500803, 
                           Party_Total=2864079, 
                           Total_527=3887021))


```


```{r}
 

UT_data <- data.frame(Utah = c(State_Donor_Total=28318572, 
                           House_Total=6948969, 
                           Senate_Total=5308229, 
                           Pres_Total=4981458,	
                           PAC_Total=7600668, 
                           Party_Total=2549352, 
                           Total_527=929896))
                           


NE_data<- data.frame(Nebraska = c(State_Donor_Total=28204165, 
                           House_Total=5074626, 
                           Senate_Total=3210223, 
                           Pres_Total=2512052,	
                           PAC_Total=12630766, 
                           Party_Total=2740898, 
                           Total_527=2035600))

```
<- data.frame( = c(State_Donor_Total=, 
                           House_Total=, 
                           Senate_Total=, 
                           Pres_Total=,	
                           PAC_Total=, 
                           Party_Total=, 
                           Total_527=))

```{r}
NH_data<- data.frame(NewHampshire = c(State_Donor_Total=23038927, 
                           House_Total=3479998, 
                           Senate_Total=6543110, 
                           Pres_Total=5411941,	
                           PAC_Total=4951825, 
                           Party_Total=2214253, 
                           Total_527=437800))


MT_data <- data.frame(Montana = c(State_Donor_Total=21884379, 
                           House_Total=4894800, 
                           Senate_Total=7136224, 
                           Pres_Total=2705228,	
                           PAC_Total=4878927, 
                           Party_Total=1885480, 
                           Total_527=383720))
 
```


```{r}

ME_data <- data.frame(Maine = c(State_Donor_Total=21478469, 
                           House_Total=2978979, 
                           Senate_Total=7452328, 
                           Pres_Total=3815162,	
                           PAC_Total=4769985, 
                           Party_Total=2089043, 
                           Total_527=372972))

ID_data <- data.frame(Idaho = c(State_Donor_Total=19882393, 
                           House_Total=2309530, 
                           Senate_Total=4257777, 
                           Pres_Total=3254479,	
                           PAC_Total=7066606, 
                           Party_Total=2463591, 
                           Total_527=530410))


MS_data <- data.frame(Mississippi = c(State_Donor_Total=19160624, 
                           House_Total=2691419, 
                           Senate_Total=5066757, 
                           Pres_Total=1986252,	
                           PAC_Total=5423992, 
                           Party_Total=2968554, 
                           Total_527=1023650))
```



```{r}

WY_data <- data.frame(Wyoming = c(State_Donor_Total=18874037, 
                           House_Total=2126563, 
                           Senate_Total=4254590, 
                           Pres_Total=1587996,	
                           PAC_Total=8269598, 
                           Party_Total=2364560, 
                           Total_527=270730))

DE_data<- data.frame(Delaware = c(State_Donor_Total=15852885, 
                           House_Total=1421959, 
                           Senate_Total=2816414, 
                           Pres_Total=4413363,	
                           PAC_Total=4852877, 
                           Party_Total=1260067, 
                           Total_527=1088205))

RI_data<- data.frame(RhodeIsland = c(State_Donor_Total=14846880, 
                           House_Total=1885133, 
                           Senate_Total=3091682, 
                           Pres_Total=2940259,	
                           PAC_Total=5305106, 
                           Party_Total=819643, 
                           Total_527=805057))
```

```{r}


AK_data<- data.frame(Alaska = c(State_Donor_Total=13598371, 
                           House_Total=2726282, 
                           Senate_Total=4799210, 
                           Pres_Total=2218300,	
                           PAC_Total=2063244, 
                           Party_Total=1460360, 
                           Total_527=330975))

HI_data<- data.frame(Hawaii = c(State_Donor_Total=13161724, 
                           House_Total=1855443, 
                           Senate_Total=3782963, 
                           Pres_Total=3291695,	
                           PAC_Total=2783995, 
                           Party_Total=1345368, 
                           Total_527=102260))

VT_data <- data.frame(Vermont = c(State_Donor_Total=10880599, 
                           House_Total=969946, 
                           Senate_Total=2705948, 
                           Pres_Total=3342556,	
                           PAC_Total=2010376, 
                           Party_Total=1298364, 
                           Total_527=553409))

```

```{r}

SD_data <- data.frame(SouthDakota = c(State_Donor_Total=10121447, 
                           House_Total=1654348, 
                           Senate_Total=2550010, 
                           Pres_Total=1204313,	
                           PAC_Total=3107459, 
                           Party_Total=1057942, 
                           Total_527=547375))

WV_data<- data.frame(WestVirginia = c(State_Donor_Total=9788086, 
                           House_Total=1538075, 
                           Senate_Total=2210540, 
                           Pres_Total=1555705,	
                           PAC_Total=3051180, 
                           Party_Total=1291486, 
                           Total_527=141100))


ND_data <- data.frame(NorthDakota = c(State_Donor_Total=9306925, 
                           House_Total=835458, 
                           Senate_Total=1344059, 
                           Pres_Total=90633,	
                           PAC_Total=4732878, 
                           Party_Total=1205203, 
                           Total_527=282995))
```

```{r}

```

```{r}
df_50 <- data.frame(AL_data, AK_data, AR_data, AZ_data, CA_data, CO_data, CT_data, DE_data, FL_data, GA_data, HI_data, ID_data, IL_data, IN_data, IA_data, KS_data, KY_data,LA_data, MA_data, MD_data, ME_data, MI_data, MN_data, MO_data, MS_data, MT_data, NC_data, ND_data, NE_data, NH_data, NJ_data, NM_data, NV_data, NY_data, OH_data, OK_data, OR_data, PA_data, RI_data, SC_data, SD_data, TN_data, TX_data, UT_data, VA_data, VT_data, WA_data, WI_data, WV_data, WY_data)
head(df_50)
```

```{r}
df_all_states <- as.data.frame(t(df_50))
df_all_states
```

```{r}
summary(df_all_states)
```

```{r}
colnames(df_all_states)[7] <- "Total_527"
df_all_states
```

```{r}
regions = c(
"Alabama",
"Alaska",
"Arizona",
"Arkansas",
'California',
'Colorado',
'Connecticut',
'Delaware',
'Florida',
'Georgia',
'Hawaii',
"Idaho",
"Illinois",
'Indiana',
"Iowa",
"Kansas",
'Kentucky',
"Louisiana",
'Maine',
'Maryland',
"Massachusetts",
"Michigan",
"Minnesota",
"Mississippi",
'Missouri',
'Montana',
'Nebraska',
"Nevada",
'New Hampshire',
'New Jersey',
'New Mexico',
'New York',
"North Carolina",
"North Dakota",
"Ohio",
'Oklahoma',
"Oregon",
'Pennsylvania',
'Rhode Island',
"South Carolina",
'South Dakota',
"Tennessee",
'Texas',
'Utah',
'Vermont',
'Virginia',
'Washington',
'West Virginia',
'Wisconsin',
"Wyoming")

region <- tolower(regions)
```


```{r}
abbr = c(
"AL",
"AK",
'AZ',
'AR',
'CA',
'CO',
'CT',
'DE',
'FL',
"GA",
'HI',
"ID",
"IL",
"IN",
'IA',
'KS',
'KY',
'LA',
'ME',
'MD',
"MA",
'MI',
'MN',
"MS",
"MO",
"MT",
"NE",
"NV",
"NH",
"NJ",
"NM",
"NY",
'NC',
'ND',
'OH',
'OK',
'OR',
'PA',
'RI',
"SC",
'SD',
"TN",
"TX",
'UT',
"VT",
'VA',
"WA",
'WV',
"WI",
"WY")
```

```{r}
df1 <- cbind(df_all_states, region, abbr, election, state_pop_2020, party_id) 
df1
```

```{r}
library(ggplot2)

ggplot(df_all_states, aes(x=abbr, y=State_Donor_Total)) +
  geom_boxplot(fill="steelblue", color="black") +
  ggtitle("Boxplot of the Donor Total")
```

```{r}
ggplot(df, aes(x=abbr, y=PAC_Total))+
  geom_col()

```

```{r}
ggplot(df, aes(y=abbr, x=Senate_Total))+
  geom_col()
```

```{r}
#install.packages("usmap")
library(usmap)
library(ggplot2)
plot_usmap(regions = "states")+
  labs(title = "U.S. States")+
  theme(panel.background = element_blank())
```


```{r}
#based on senate map 2022 and electoral map 2020
party_id = c(
AL=1,
AK=1,
AZ=0,
AR=1,
CA=0,
CO=0,
CT=0,
DE=0,
FL=1,
GA=1,
HI=0,
ID=1,
IL=0,
IN=1,
IA=1,
KS=1,
KY=1,
LA=1,
ME=0,
MD=0,
MA=0,
MI=0,
MN=0,
MS=1,
MO=1,
MT=1,
NE=1,
NV=0,
NH=0,
NJ=0,
NM=1,
NY=0,
NC=1,
ND=1,
OH=1,
OK=1,
OR=0,
PA=1,
RI=0,
SC=1,
SD=1,
TN=1,
TX=1,
UT=1,
VT=0,
VA=0,
WA=0,
WV=1,
WI=1,
WY=1
)


```
```{r}
party = c(Republican = 1, Democrat =1)


election <- c("alabama"=Republican,
             "alaska"=Republican,
             "arizona"=Democrat,       "arkansas"=Republican,"california"=Democrat,"colorado"=Democrat,"connecticut"=Democrat,"delaware"=Democrat,"florida"=Republican,"georgia"=Republican,"hawaii"=Democrat,    "idaho"=Republican,"illinois"=Democrat,"indiana"=Republican,"iowa"=Republican,"kansas"=Republican, "kentucky"=Republican,"louisiana"=Republican,"maine"=Democrat,         "maryland"=Democrat,"massachusetts"=Democrat,"michigan"=Democrat,"minnesota"=Democrat,"mississippi"=Republican,"missouri"=Republican,"montana"=Republican,"nebraska"=Republican,"nevada"=Democrat,"new hampshire"=Democrat,"new jersey"=Democrat,"new mexico"=Republican,"new york"=Democrat,"north carolina"=Republican,"north dakota"=Republican,"ohio"=Republican,"oklahoma"=Republican,"oregon"=Democrat,"pennsylvania"=Republican,"rhode island"=Democrat,"south carolina"=Republican,"south dakota"=Democrat,"tennessee"=Republican,"texas"=Republican,"utah"=Republican,
"vermont"=Republican,"virginia"=Republican,"washington"=Democrat,"west virginia"=Republican, "wisconsin"=Republican, "wyoming"=Republican
)
```


library(usmap)
library(ggplot2)

dfmaps <- data.frame(
  states=c("AL",
"AK",
'AZ',
'AR',
'CA',
'CO',
'CT',
'DE',
'FL',
"GA",
'HI',
"ID",
"IL",
"IN",
'IA',
'KS',
'KY',
'LA',
'ME',
'MD',
"MA",
'MI',
'MN',
"MS",
"MO",
"MT",
"NE",
"NV",
"NH",
"NJ",
"NM",
"NY",
'NC',
'ND',
'OH',
'OK',
'OR',
'PA',
'RI',
"SC",
'SD',
"TN",
"TX",
'UT',
"VT",
'VA',
"WA",
'WV',
"WI",
"WY"),
values = c(1,1,0,1,0,0,0,0,1,1,0,1,0,1,1,1,1,1,0,0,0,0,0,1,1,1,1,0,0,0,1,0,1,1,1,1,0,1,0,1,1,1,1,1,0,0,0,1,1,1))
plot_usmap(data = df, values=values)
 
 
  


```{r}
plot_usmap(regions = "states") + 
  labs(title = "U.S. States",
       subtitle = "This is a blank map of the United States.") + 
  theme(panel.background=element_blank())
```

```{r}
library(readxl)
t_elec_19 <- read_excel("~/Desktop/Final Paper:Project/t_elec_19.xls")
View(t_elec_19)
```

```{r}
df_election19 <- data.frame(t_elec_19)

dim(df_election19)
```

```{r}
#library(DataExplorer)

#create_report(df2)
```


```{r}
df_full <- merge(df, df_election19)

#df_full
```

```{r}
library(DataExplorer)
```

```{r}
library(ggplot2)
library(maps)

party_colors <- c("#2E74C0", "#CB454A") 

ggplot(election_df, aes(x = party_id, y = State_Donor_Total)) + 
  geom_point(aes(size = .5, color = "blue")) + 
  geom_smooth(method = 'lm',formula = y ~ x)  # Add regression line

```


```{r}
library(usdata)

data.frame(state_stats)

```


```{r}
state_pop_2020 = c(
AL=5024279,
AK=733391,
AZ=7151502,
AR=3011524,
CA=39538223,
CO=5773714,
CT=3605944,
DE=989948,
FL=21538187,
GA=10711908,
HI=1455271,
ID=1839106,
IL=12801989,
IN=6785528,
IA=3271616,
KS=2937880,
KY=4505836,
LA=4657757,
ME=1362359,
MD=6177224,
MA=7029917,
MI=10077331,
MN=5706494,
MS=2961279,
MO=6154913,
MT=1084225,
NE=1961504,
NV=3104614,
NH=1377529,
NJ=9288994,
NM=2117522,
NY=20201249,
NC=10439388,
ND=779094,
OH=11799448,
OK=3959353,
OR=4237256,
PA=13002700,
RI=1097379,
SC=5118425,
SD=886667,
TN=6910840,
TX=29145505,
UT=3205958,
VT=643077,
VA=8631393,
WA=7705281,
WV=1793716,
WI=5893718,
WY=576851
)
```

```{r}
ggplot(election_df, aes(x = party_id, y = PAC_Total)) + 
  geom_point(aes(size = .5, color = "blue")) + 
  geom_smooth(method = 'lm',formula = y ~ x)  # Add regression line


```
```{r }
summary.data.frame(df)
```

```{r}
ggplot(df, 
       aes(x = abbr, 
           fill = State_Donor_Total)) + 
  geom_bar(position = "stack")
```

```{r}
ggplot(df, aes(x = state_pop_2020)) +
  geom_histogram() + 
  labs(title = "State Donor Total by Population",
       x = "state_pop_2020")
```

```{r}
library(GGally)
plot(df1)
```

```{r}
library(maps)
library(ggthemes)
library(cowplot)


party_colors <- c("#2E74C0", "#CB454A") 
ggplot(data = df2,
             mapping = aes(x = long, y = lat,
                          group = group, fill = party_id))+ 
  geom_polygon(color = "gray90", size = 0.1)+
  coord_map(projection = "albers", lat0 = 39, lat1 = 45)+ 
  scale_fill_manual(values = party_colors)+
  labs(title = "State Party ID", fill = NULL)+ 
  theme_map()
```


```{r}
summary(df)
 
```




```{r}
library(dplyr)
library(plyr)
library(maps)
```


```{r}
election_df <- merge(us_states, df1, sort=FALSE)
election_df
```


```{r}
p <- ggplot(data = us_states,
            mapping = aes(x = long, y = lat,
                          group = group))

p + geom_polygon(fill = "white", color = "black")
```


```{r}
str(election_df)

```

```{r}
lm(formula = formula(df), data = df)

```


```{r}
library(dlookr)
eda_web_report(df) 
```

```{r}
library(tikzDevice)

```

